Source Summaries

### 2020-04-26 paper/sourceSummaries/summary10.tex
Added joshua's 10th source summary

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{{R}everse {E}ngineering the {C}ommunications {P}rotocol of an {RFID} {P}ublic {T}ransportation {C}ard}

@@

\Urlmuskip=0mu plus 1mu\relax
%remove % to show citation, change the name to your entry
\bibentry{7945583}

@@

\noindent
The authors use a ProxMark 3 to investigate the feasibility of cloning a two different variants of public transport metro cards used in major cities.  Both public trasnport cards were from cities based in Spain.

@@

\noindent
Game Theory.  The authors use weaknesses in smart card protocols to allow for easy cloning.

@@

\noindent
The authors use a ProxMark 3 RDV to actively scan for RFID cards using a long-range RFID antenna and a ProxMark connected to a laptop in a backpack.

@@

\noindent
The authors did not find a major security issue in the RFID cards they were testing, but instead were concerned with the fact that all communication was done over cleartext channels.

@@

\noindent
The authors note that Near Field Communication is partially compatible, and that an Android device may add some interest to future research.
